\section{Motivation}
\label{sec:motivation}

With the widespread use of commodity hardware in many systems such as
the Google File System \cite{GFS}, error recovery has become the new
focus. In environments such as these errors and failures are accepted
as the norm and error recovery techniques become the critical
components of the system. For a system employing block level caching
failures in the system would mean fetching blocks from network storage
all over again and attempting to get the system back to its previous
state so it can continue its task. We wish to mitigate this issue by
allowing easy recovery of a cache in the event of a failure this way
nodes that have failed can continue their tasks from where they left
off with minimal recovery overhead.

Recovering the data that was already present in the cache would
mitigate recovery time since the cache will already be warm which
means that blocks that the system was caching before the failure would
once again be available rather than having to be fetched from remote
storage again. Fault tolerance comes at a cost though, because there
needs to be a way to store data persistently somewhere this mechanism
would add overhead but with emerging SSD technology and the response
time and throughput of SSD's the overhead that would be incurred under
normal operation is acceptable in some cases if it guarantees quick
recovery from a failure.

While the issue of the overhead comes into play when it comes to
performance we believe that certain workloads with lower throughput
requirements. For read heavy workloads where the cache is warmed up
and not modified very often the cache with metadata persistence should
perform the same as the cache with no persistence while still having
the added benefit of being able to recover from failure.
